Creating the ``r params$package_name`` R package

### 2025-12-30 create-FSHybridPLS.Rmd
changed get_rho

```{r}
#' Compute PLS Scores
#'
#' Projects the hybrid predictor data W onto the weight direction defined by d_vec
#' to calculate the PLS scores.
#'
#' @param d_vec A numeric vector of concatenated coefficients (functional basis coeffs + scalar weights).
#' @param W A `predictor_hybrid` object containing the data.
#'
#' @return A numeric vector of PLS scores (length n).
#' @export
get_rho <- function(d_vec, W) {
  K <- W$n_functional
  M <- W$n_basis_list[[1]] # Assumes same number of basis functions for all K
  n_scalar <- W$n_scalar
  n <- W$n_sample

  # Initialize rho vector
  rho <- rep(0, n)

  # --- Functional Part ---
  # Iterate over functional predictors to compute inner products <X^(k), gamma^(k)>
  for (j in 1:K) {
    # Extract coefficients for the j-th functional weight
    start_index <- (j - 1) * M + 1
    end_index <- j * M
    gamma_j <- d_vec[start_index:end_index]

    # Get data coefficients (samples x basis)
    Theta_j <- t(W$functional_list[[j]]$coefs)

    # Gram matrix
    B <- W$gram_list[[j]]

    # Update scores: rho += Theta * B * gamma
    # (samples x basis) * (basis x basis) * (basis x 1) -> (samples x 1)
    rho <- rho + Theta_j %*% (B %*% gamma_j)

  }

  # --- Scalar Part ---
  # Extract scalar weights (the remaining coefficients in d_vec)
  scalar_indices <- (K * M + 1):length(d_vec)
  scalar_weights <- d_vec[scalar_indices]

  # Update scores: rho += Z * weights
  rho <- rho + W$Z %*% scalar_weights

  return(as.vector(rho))
}
```

@@

  return(list(
    rho = rho,
    xi = xi,
    beta = beta,
    validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL
  ))
}
```

>>>>

```{r}
#' Exact Hybrid Inner Product
#' Computes <W, xi> using basis inner product matrices.
#' @param W The hybrid predictor object (contains coefs for N samples)
#' @param xi The hybrid weight object (contains coefs for 1 direction)
#' @return A vector of scores (length N)
get_rho <- function(W, xi) {

  # 1. Scalar Part (Standard dot product)
  # (N x p_scalar) %*% (p_scalar x 1)
  scores <- as.matrix(W$Z) %*% as.matrix(xi$Z)

  # 2. Functional Part (Basis Matrix Algebra)
  # Loop through each functional variable
  for(k in seq_along(W$functional_list)) {

    # Extract basis and coefficients
    # Coefs_W is (Basis_Dim x N)
    # Coefs_xi is (Basis_Dim x 1)
    fd_W  <- W$functional_list[[k]]
    fd_xi <- xi$functional_list[[k]]

    # A. Compute J Matrix (Basis Inner Product)
    # J[i,j] = Integral(phi_i(t) * phi_j(t) dt)
    # Note: computed once per variable, very fast for B-splines
    J <- fda::inprod(fd_W$basis, fd_W$basis)

    # B. Compute Integral via Matrix Multiplication
    # Formula: Score = Coefs_W^T * J * Coefs_xi
    # Dimensions: (N x B) * (B x B) * (B x 1) -> (N x 1)

    # Optimization: Pre-multiply J * xi to get a "weighted weight"
    weighted_xi <- J %*% fd_xi$coefs

    # Project data onto this weighted weight
    scores <- scores + t(fd_W$coefs) %*% weighted_xi
  }

  return(as.vector(scores))
}
```

@@

  return(list(
    rho = rho,
    xi = xi,
    beta = beta,
    W = W_now,
    delta = delta,
    nu = nu,
    validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL
  ))
}
```
